---
title: "julia_test_code"
output: html_document
---

```{r, warning=FALSE, message=FALSE}
library(mdsr)
library(RMySQL)
db <- dbConnect_scidb(dbname = "imdb")
```

Make query to get number of productions for top 10 trans actors
```{r, eval = FALSE}
db %>%
  dbGetQuery("SELECT name, COUNT(DISTINCT movie_id) AS 'Number of movies acted in'
              FROM name n
              LEFT JOIN cast_info c ON n.id = c.person_id
              WHERE n.name IN ('Cox, Laverne', 'Ervin, Erika', 'Bono, Chaz', 'Lepore, Amanda', 'Lazzarato, Gigi', 'Carrera, Carmen', 'Wachowski, Lana', 'Lysette, Trace', 'Jenner, Caitlyn', 'Arquette, Alexis')
              GROUP BY n.name
              ORDER BY COUNT(DISTINCT c.movie_id) DESC
                ;")
```

Name | Number of movies acted in
--|--
Jenner, Caitlyn | 450
Cox, Laverne | 217
Bono, Chaz | 140
Arquette, Alexis | 117
Wachowski, Lana | 62
Carrera, Carmen | 61
Lepore, Amanda | 44
Ervin, Erika | 37
Lazzarato, Gigi | 29
Lysette, Trace | 25


List of prominent trans actors:
```{r}
trans_act_10 <- c("Cox, Laverne", "Ervin, Erika", "Bono, Chaz", "Lepore, Amanda", "Lazzarato, Gigi", "Carrera, Carmen", "Wachowski, Lana", "Wachowski, Lilly", "Lysette, Trace", "Jenner, Caitlyn")
```

Query with number of productions for top ten non-trans actors:
https://www.ranker.com/crowdranked-list/the-greatest-film-actors-and-actresses-of-all-time

```{r}
db %>%
  dbGetQuery("SELECT name, COUNT(DISTINCT movie_id) AS 'Number of movies acted in'
              FROM name n
              LEFT JOIN cast_info c ON n.id = c.person_id
              WHERE n.name IN ('Hanks, Tom', 'Davis, Bette', 'Nicholson, Jack', 'Brando, Mark', 'De Niro, Robert', 'Hepburn, Katharine', 'Stewart, James', 'Hopkins, Anthony', 'Hoffman, Dustin', 'Hepburn, Audrey')
              GROUP BY n.name
              ORDER BY COUNT(DISTINCT c.movie_id) DESC
                ;")
```

From imdb: https://www.imdb.com/list/ls004429898/
```{r}
db %>%
  dbGetQuery("SELECT name, COUNT(DISTINCT movie_id) AS 'Number of movies acted in'
              FROM name n
              LEFT JOIN cast_info c ON n.id = c.person_id
              WHERE n.name IN ('Willis, Bruce', 'Depp, Johnny', 'Oldman, Gary', 'Hanks, Tom', 'Lee Jones, Tommy', 'Smith, Will', 'Alba, Jessica', 'Hayek, Salma', 'Cruz, Penelope', 'Gabin, Jean', 'de Funès, Louis')
              GROUP BY n.name
              ORDER BY COUNT(DISTINCT c.movie_id) DESC
                ;")
```

Name | Number of movies acted in
--|--
Hanks, Tom | 1142
Stewart, James | 923
De Niro, Robert | 605
Hoffman, Dustin | 505
Hopkins, Anthony | 481
Davis, Bette | 387
Nicholson, Jack | 317
Hepburn, Audrey | 204
Hepburn, Katharine | 170

List of other actors with similar number of productions:
```{r, eval = FALSE}
db %>%
  dbGetQuery("SELECT name, COUNT(DISTINCT movie_id) AS 'Number of movies acted in'
              FROM name n
              LEFT JOIN cast_info c ON n.id = c.person_id
              GROUP BY n.id
              HAVING COUNT(DISTINCT movie_id) = 450
              LIMIT 4
                ;")
```

Name | Number of movies acted in
--|--
Arangüena, Ramón; Aylesworth, John; Beach, John | 450
Agassi, Carlos; Alboreto, Michele; Alderson, Erville | 217
Aldama, Jorge; Algueró, Augusto; Alkin, John | 140
Acord, Art; Ade, George; Adell, Ilunga | 117
Abdel Aziz, Mahmoud; Abecasis, Chiqui; Abhishek, Krishna | 62
Aagesen, Elias Amati; Abbey, Francis; Abrahamsson, Magnus | 61
Aaron, Nicholas, Abad, Javier; Abed, Ramzi | 44
Aaron, Jonne; Abaydulov, Gali; Abel, Lucas | 37
Abadía, Miguel Ángel; Abbate, Jessie; Abbott Jr., Michael | 29
Aakre, Even ; Abad Ojuel, Antonio; Abadia, Lysander| 25


Salaries of each:

...So it's a lot harder than I anticipated to find their salaries  
Use imdb gross something or another instead? 

```{r}
db %>%
  dbGetQuery("
SELECT name, COUNT(DISTINCT movie_id) AS 'Avg of movies acted in',
AVG(i.info REGEXP 'gross')
FROM imdb.name n
LEFT JOIN cast_info c ON n.id = c.person_id
LEFT JOIN person_info p ON n.id = p.person_id
LEFT JOIN info_type i ON p.info_type_id = i.id
GROUP BY n.id
HAVING COUNT(DISTINCT movie_id) = 20
LIMIT 3;")
```


Make a plot:

```{r}
rank <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10,)
num <- c(217, 37, 140, 44, 29, 61, 62, 25, 450, 117, 577, 690, 254, 1142, 1392, 523, 489, 1, 148, 221)
id <- c("t", "t", "t", "t", "t","t", "t", "t", "t", "t", "n", "n", "n", "n", "n", "n", "n", "n", "n", "n")
trans_num <- c(217, 37, 140, 44, 29, 61, 62, 25, 450, 117)
nont_num <- c(577, 690, 254, 1142, 1392, 523, 489, 1, 148, 221)

df <- data.frame(rank, trans_num, nont_num)
df2 <- data.frame(rank, num, id)

ggplot(df2, aes(x = rank, y = num, fill = id)) +
  geom_col(position=position_dodge(), width = .9) +
 # geom_smooth(method = "loess", se = FALSE, aes(color = id)) +
  xlab("IMDB rank") +
  ylab("Number of movie productions") +
  scale_fill_discrete(name = "Identity", labels = c("non-trans", "trans")) +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)) +
  scale_y_continuous(breaks = c(0, 250, 500, 750, 1000, 1250, 1500)) +
  geom_text(aes(label = num), nudge_x= -0.2, size = 3)
```

```{r}
#average number of productions for top-ten trans actors
# = 118.2
df2 %>%
  filter(id == "t") %>%
  summarize(avg_productions = mean(num))

#average number of productions for top-ten non-trans actors
df2 %>%
  filter(id == "n") %>%
  summarize(avg_productions = mean(num))
# = 543.7


produc <- c(543.7, 118.2)
ids <- c("nontrans", "trans")
df3 <- data.frame(produc, ids)

ggplot(df3, aes(x = ids, y = produc, fill = ids)) +
  geom_col(width = .9) +
  ylab("Average number of movie productions") +
  xlab("Identity") +
  guides(fill=FALSE) +
  scale_y_continuous(breaks = c(0, 100, 200, 300, 400, 500)) +
  geom_text(aes(label = produc), nudge_y = -20, size = 4)

```

