---
title: "julia_test_code"
output: html_document
---

```{r, warning=FALSE, message=FALSE}
library(mdsr)
library(RMySQL)
db <- dbConnect_scidb(dbname = "imdb")
```

Make query to get number of productions for top 10 trans actors
```{r, eval = FALSE}
db %>%
  dbGetQuery("SELECT name, COUNT(DISTINCT movie_id) AS 'Number of movies acted in'
              FROM name n
              LEFT JOIN cast_info c ON n.id = c.person_id
              WHERE n.name IN ('Cox, Laverne', 'Ervin, Erika', 'Bono, Chaz', 'Lepore, Amanda', 'Lazzarato, Gigi', 'Carrera, Carmen', 'Wachowski, Lana', 'Lysette, Trace', 'Jenner, Caitlyn', 'Arquette, Alexis')
              GROUP BY n.name
              ORDER BY COUNT(DISTINCT c.movie_id) DESC
                ;")
```

Name | Number of movies acted in
--|--
Jenner, Caitlyn | 450
Cox, Laverne | 217
Bono, Chaz | 140
Arquette, Alexis | 117
Wachowski, Lana | 62
Carrera, Carmen | 61
Lepore, Amanda | 44
Ervin, Erika | 37
Lazzarato, Gigi | 29
Lysette, Trace | 25


List of prominent trans actors:
```{r}
trans_act_10 <- c("Cox, Laverne", "Ervin, Erika", "Bono, Chaz", "Lepore, Amanda", "Lazzarato, Gigi", "Carrera, Carmen", "Wachowski, Lana", "Wachowski, Lilly", "Lysette, Trace", "Jenner, Caitlyn")
```

List of other actors with similar number of productions:
```{r, eval = FALSE}
db %>%
  dbGetQuery("SELECT name, COUNT(DISTINCT movie_id) AS 'Number of movies acted in'
              FROM name n
              LEFT JOIN cast_info c ON n.id = c.person_id
              GROUP BY n.id
              HAVING COUNT(DISTINCT movie_id) = 450
              LIMIT 4
                ;")
```

Name | Number of movies acted in
--|--
Arangüena, Ramón; Aylesworth, John; Beach, John | 450
Agassi, Carlos; Alboreto, Michele; Alderson, Erville | 217
Aldama, Jorge; Algueró, Augusto; Alkin, John | 140
Acord, Art; Ade, George; Adell, Ilunga | 117
Abdel Aziz, Mahmoud; Abecasis, Chiqui; Abhishek, Krishna | 62
Aagesen, Elias Amati; Abbey, Francis; Abrahamsson, Magnus | 61
Aaron, Nicholas, Abad, Javier; Abed, Ramzi | 44
Aaron, Jonne; Abaydulov, Gali; Abel, Lucas | 37
Abadía, Miguel Ángel; Abbate, Jessie; Abbott Jr., Michael | 29
Aakre, Even ; Abad Ojuel, Antonio; Abadia, Lysander| 25


Salaries of each:

...So it's a lot harder than I anticipated to find their salaries  
Use imdb gross something or another instead? 
