---
title: "Draft"
author: "Mylo"
date: "4/25/2018"
output: html_document
---

Just testing git :)
```{r}
library(dplyr)
```

Gender IS Binary 
```{r}
db<- dbConnect_scidb(dbname="imdb")
dbGetQuery("Select name, gender 
From name
Where gender=NULL;"
)
```

gender is still binary 
```{r}
dbGetQuery("Select COUNT(DISTINCT gender) From name;")
```

Some examples of correctly listed trans folks: 
Select name, gender
From name
where name= "Lepore, Amanda"

Select name, gender
From name
where name= "Bono, Chaz"

Non-Binary Person listed as Male 

Select name, gender
From name
where name= "Spoon, Rae"

Aja: many outputs
Select name, gender
From name
where name= "aja"


Finding all the trans folks --- Takes some time to run
now that we have this, we can take the person ID numbers and pull those numbers from the name list to get a solid list of trans actors in the IMDB

```{r}
dbGetQuery(
"Select *
From person_info
WHERE info LIKE "%trans%" ANd
info is not NULL and
info not LIKE "%transa%" and
info not LIKE "%transb%" and
info not LIKE "%transc%" and
info not LIKE "%transd%" and
info not LIKE "%transe%" and
info not LIKE "%transh%" and
info not LIKE "%transi%" and
info not LIKE "%transj%" and
info not LIKE "%transk%" and
info not LIKE "%transl%" and
info not LIKE "%transn%" and
info not LIKE "%transo%" and
info not LIKE "%transp%" and
info not LIKE "%transq%" and
info not LIKE "%transr%" and
info not LIKE "%transt%" and
info not LIKE "%transu%" and
info not LIKE "%transv%" and
info not LIKE "%transw%" and
info not LIKE "%transx%" and
info not LIKE "%transy%" and
info not LIKE "%transz%" and
info not LIKE "%transac%" and
info not Like "%trans-racial%" and 
info not LIKE "%transp%" and
info not LIKE "%transi%" and 
info not LIKE "%transc%" and
info not Like "trans media%" and
info not like "%transfix%" and
info not like "%trans-atlantic%" and
info not LIKE "%transy%" and 
info not LIKE "%transfer%" and 
info not LIKE "%transfo%" and 
info not LIKE "%transat%" and 
info not LIKE "%transgre%" and 
info not LIKE "%transmu%" and 
info not LIKE "%transmit%" and
info not LIKE "%transGr%" and
info not LIKE "%transfigu%" and
info not LIKE "%transwor%" and
info not LIKE "%transmis%" and
info not LIKE "%transeau%" and
info not LIKE "%transk%" and
info not LIKE "%translu%" and
info not LIKE "%transfus%" and
info not LIKE "%transmalians%" and
info not LIKE "%trans-am%" and
info not LIKE "%Autrans%" and
info not LIKE "%trans canada%" and
info not LIKE "%trans-siberian%" and
info not LIKE "%trans national%" and
info not LIKE "%transmigr%" and
info not LIKE "%transtra%" and
info not LIKE "%transequr%" and
info not LIKE "%transue%" and
info not LIKE "%trans.%" and
info not LIKE "%transom%" and
info not LIKE "%transpar%" and
info not LIKE "%transmed%" and
info not LIKE "%transs%" and 
info not LIKE "%transv%" and 
info not LIKE "%translat%" and
info not LIKE "%transnati%" and
info not LIKE "%transmetr%" and
info not LIKE "%transfer%" and
info not LIKE "%transfa%" and
info not LIKE "%transl%";"
)
```



