---
title: "Draft"
author: "Mylo"
date: "4/25/2018"
output: html_document
---

Just testing git :)
```{r}
library(tidyverse)
library(mdsr)
library(RMySQL)
db <- dbConnect_scidb(dbname = "imdb")
```

Gender IS Binary 
```{r}
dbGetQuery("Select name, gender 
From name
Where gender=NULL;")
```

gender is still binary 
```{r}
dbGetQuery("Select COUNT(DISTINCT gender) From name;")
```

Some examples of correctly listed trans folks: 
Select name, gender
From name
where name= "Lepore, AmANDa"

Select name, gender
From name
where name= "Bono, Chaz"

Non-Binary Person listed as Male 

Select name, gender
From name
where name= "Spoon, Rae"

Aja: many outputs
Select name, gender
From name
where name= "aja"


Finding all the trans folks --- Takes some time to run
now that we have this, we can take the person ID numbers AND pull those numbers from the name list to get a solid list of trans actors in the IMDB

```{r}
trans_actors_whole_info<- db %>% 
  dbGetQuery(" Select *
FROM name
JOIN person_info on person_info.person_id= name.id
WHERE info LIKE '%trans%' AND
info is not NULL AND
info not LIKE '%transa%' AND
info not LIKE '%transb%' AND
info not LIKE '%transc%' AND
info not LIKE '%transd%' AND
info not LIKE '%transe%' AND
info not LIKE '%transh%' AND
info not LIKE '%transi%' AND
info not LIKE '%transj%' AND
info not LIKE '%transk%' AND
info not LIKE '%transl%' AND
info not LIKE '%transn%' AND
info not LIKE '%transo%' AND
info not LIKE '%transp%' AND
info not LIKE '%transq%' AND
info not LIKE '%transr%' AND
info not LIKE '%transt%' AND
info not LIKE '%transu%' AND
info not LIKE '%transv%' AND
info not LIKE '%transw%' AND
info not LIKE '%transx%' AND
info not LIKE '%transy%' AND
info not LIKE '%transz%' AND
info not LIKE '%transac%' AND
info not Like '%trans-racial%' AND 
info not LIKE '%transp%' AND
info not LIKE '%transi%' AND 
info not LIKE '%transc%' AND
info not Like '%trans media%' AND
info not like '%transfix%' AND
info not like '%trans-atlantic%' AND
info not LIKE '%transy%' AND 
info not LIKE '%transfer%' AND 
info not LIKE '%transfo%' AND 
info not LIKE '%transat%' AND 
info not LIKE '%transgre%' AND 
info not LIKE '%transmu%' AND 
info not LIKE '%transmit%' AND
info not LIKE '%transGr%' AND
info not LIKE '%transfigu%' AND
info not LIKE '%transwor%' AND
info not LIKE '%transmis%' AND
info not LIKE '%transeau%' AND
info not LIKE '%transk%' AND
info not LIKE '%translu%' AND
info not LIKE '%transfus%' AND
info not LIKE '%transmalians%' AND
info not LIKE '%trans-am%' AND
info not LIKE '%Autrans%' AND
info not LIKE '%trans canada%' AND
info not LIKE '%trans-siberian%' AND
info not LIKE '%trans national%' AND
info not LIKE '%transmigr%' AND
info not LIKE '%transtra%' AND
info not LIKE '%transequr%' AND
info not LIKE '%transue%' AND
info not LIKE '%trans.%' AND
info not LIKE '%transom%' AND
info not LIKE '%transpar%' AND
info not LIKE '%transmed%' AND
info not LIKE '%transs%' AND 
info not LIKE '%transv%' AND 
info not LIKE '%translat%' AND
info not LIKE '%transnati%' AND
info not LIKE '%transmetr%' AND
info not LIKE '%transfer%' AND
info not LIKE '%transfa%' AND
info not LIKE '%transl%';")
```



