---
title: "Gender? In the IMDB? It's more likely than you might think."
author: "Julia, Mylo, Nashshaba"
date: "4/25/2018"
output: 
  html_document:
    code_folding: hide
---

###Problem Statement:

The *International Movie Database (IMDB)*  is a well known internet database containing. Society imposes binary gender options on individuals, so we explored how this manifests in the data stored with the *IMDB*. 


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(mdsr)
library(RMySQL)
db <- dbConnect_scidb(dbname = "imdb")
```

###Analysis: 

#####Gender IS Binary:

To begin our exploration of gender and its appearance in the *IMDB*, we utilized a function to count distinct options for the ‘Gender’ column of the ‘Names’ table.  The return on this endeavor was 2, which indicates the IMDB is still enforcing the gender binary. 

```{r message=FALSE, warning=FALSE}
db %>% 
dbGetQuery("Select COUNT(DISTINCT gender) 
           From name;")
```

#####Finding Transgender people in the IMDB:

The next stage of our analysis focused on trying to find actors that identify as trans from the IMDB.  The only column that contained the words trans, transgender, transfem, transmasc, etc, were located in the ‘notes’ column for person_info. We joined the ‘person_info’ and ‘name’ columns to produce a table that included the ‘notes’ and ‘names’ column.  This enabled the filtering out of trans identified individuals present in the database. It was really hard to separate words involving gender from other words spelled with ‘trans’, such as “transform”, “transport”, “transfuse”, and “trans-atlantic”. The table we ended up with also includes cis folks that have acted in trans roles (also problematic).  The IMDB participates in trans erasure to some degree.  It should not have been this difficult to find trans actors in a database. 

The table below shows a one random actor from the data set created in this process:

```{r message=FALSE, warning=FALSE}
trans_actors_whole_info <- db %>% 
  dbGetQuery(" Select gender, name, note, person_id, info
FROM name
JOIN person_info on person_info.person_id= name.id
WHERE info LIKE '%trans%' AND
info is not NULL AND
info not LIKE '%transa%' AND
info not LIKE '%transb%' AND
info not LIKE '%transc%' AND
info not LIKE '%transd%' AND
info not LIKE '%transe%' AND
info not LIKE '%transh%' AND
info not LIKE '%transi%' AND
info not LIKE '%transj%' AND
info not LIKE '%transk%' AND
info not LIKE '%transl%' AND
info not LIKE '%transn%' AND
info not LIKE '%transo%' AND
info not LIKE '%transp%' AND
info not LIKE '%transq%' AND
info not LIKE '%transr%' AND
info not LIKE '%transt%' AND
info not LIKE '%transu%' AND
info not LIKE '%transv%' AND
info not LIKE '%transw%' AND
info not LIKE '%transx%' AND
info not LIKE '%transy%' AND
info not LIKE '%transz%' AND
info not LIKE '%transac%' AND
info not Like '%trans-racial%' AND 
info not LIKE '%transp%' AND
info not LIKE '%transi%' AND 
info not LIKE '%transc%' AND
info not Like '%trans media%' AND
info not like '%transfix%' AND
info not like '%trans-atlantic%' AND
info not LIKE '%transy%' AND 
info not LIKE '%transfer%' AND 
info not LIKE '%transfo%' AND 
info not LIKE '%transat%' AND 
info not LIKE '%transgre%' AND 
info not LIKE '%transmu%' AND 
info not LIKE '%transmit%' AND
info not LIKE '%transGr%' AND
info not LIKE '%transfigu%' AND
info not LIKE '%transwor%' AND
info not LIKE '%transmis%' AND
info not LIKE '%transeau%' AND
info not LIKE '%transk%' AND
info not LIKE '%translu%' AND
info not LIKE '%transfus%' AND
info not LIKE '%transmalians%' AND
info not LIKE '%trans-am%' AND
info not LIKE '%Autrans%' AND
info not LIKE '%trans canada%' AND
info not LIKE '%trans-siberian%' AND
info not LIKE '%trans national%' AND
info not LIKE '%transmigr%' AND
info not LIKE '%transtra%' AND
info not LIKE '%transequr%' AND
info not LIKE '%transue%' AND
info not LIKE '%trans.%' AND
info not LIKE '%transom%' AND
info not LIKE '%transpar%' AND
info not LIKE '%transmed%' AND
info not LIKE '%transs%' AND 
info not LIKE '%transv%' AND 
info not LIKE '%translat%' AND
info not LIKE '%transnati%' AND
info not LIKE '%transmetr%' AND
info not LIKE '%transfer%' AND
info not LIKE '%transfa%' AND
info not LIKE '%transl%';")

trans_actors_whole_info %>%
  slice(174)
```

The gender of well known actors like Laverne Cox [^1] and Caitlyn Jenner[^2] are listed correctly, but for less known trans actors gendered labeling becomes more complex.  There is not a clear and consistent way that gender is assigned to non-binary actors.   Additionally a number of trans actors were listed multiple times with any combination of F, M, and Null.  The gender for Joanna Fang [^3], a transgender woman, is listed as NA in the table above.

Another example of this strange gender record keeping is Aja, a drag performer.  Aja is listed 6 times and, one of which the gender is marked M.  

```{r message=FALSE, warning=FALSE}
db %>% 
  dbGetQuery("Select name, gender
        From name
        where name= 'aja'")
```

[^1] [Link to Laverne Cox's IMDB page](https://www.imdb.com/name/nm1209545/?ref_=nv_sr_1)
[^2] [Link to Caitlyn Jenner's IMDB page](https://www.imdb.com/name/nm0421063/?ref_=nv_sr_1)
[^3] [Link to Joanna Fang's IMDB Page](https://www.imdb.com/name/nm4825197/)





